The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-03 paper/ms.tex
conclusions paragraph

% pretty good sample

>>>>

% pretty good sample
We have presented an updated method for halo photometry, and used this to obtain light curves of 161~stars in \ktwo that were too saturated to be otherwise retrievable. These ubiquitously show variability, and we have presented global asteroseismic analysis of 31~red giants and variability classifications for all stars. This is a unique legacy sample for \ktwo, dramatically increasing the number of very bright stars that have been characterized with high-precision, rapid-time-cadence space photometry. We hope that our data release will be used for a variety of astrophysical investigations.
